### 2025-01-11 sections/4-results.tex
added plots of distance counts

>>>>

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_throughput.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:fashion-mnist-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_counts.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:glove-25-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_throughput.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:sift-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_counts.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:random-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_throughput.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:silva-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_counts.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:radioml-counts-counts}
    \end{subfigure}%
    \caption{Number of distance computations across four clustering strategies and three search algorithms on the Fashion-Mnist dataset.
    Adding the instrumentation to count the number of distance computations had the side-effect of significantly slowing down the search algorithms compared to those reported in Figure~\ref{fig:results:scaling-plots}.
    The left column shows the throughput in queries per second, while the right column shows the mean number of distance computations per query.
    The x-axis represents increasing cardinality of the dataset.}
    \label{fig:results:distance-counts}
\end{figure}
